Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-17 prob.tex
Revert commit 78c558c, because I forget cross product might not be normalized...

\yutsung{

\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
\begin{proof}
~

\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}}$,
$\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathbb{C}S^{2}$. Consider
the real vector space spanned by them, and $S^{1}$ be its unit sphere,
i.e., 
\[
\left\{ \sum_{i=0}^{2}a_{i}\ket{\psi_{i}}\middle|a_{i}\in\mathbb{R}\textrm{ and }\sideset{_{\mathbb{R}}}{_{i=0}^{2}}\sum\left|\alpha_{i}\right|^{2}=1\right\} \textrm{ .}
\]

\begin{itemize}
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
Direct from theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
\end{proof}
\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
form an orthonormal basis, and the restriction of $f$ on the real
vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$.

where the last inequality holds because $\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\in\mathbb{C}S^{1}$
is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
and 
\[
\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
\]

This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.
\end{proof}
\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\end{proof}
}

>>>>

\yutsung{\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}}

\yutsung{
\begin{proof}
~

\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\sum_{i=0}^{2}\ket{i}\ip{i}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\sum_{i=1}^{2}\ket{i}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{i}{\psi}}{\left|\ip{i}{\psi}\right|}\left|\ip{i}{\psi}\right|\right)\right|
\end{eqnarray*}
In order to estimate the last equation, we need to verify the conditions
listed in theorem~\ref{thm:analogTheorem23RichmanBridges1999}.

First, $\ket{0}$, $\ket{1'}=\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}$,
and $\ket{2'}=\ket{2}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{2}{\psi}}{\left|\ip{2}{\psi}\right|}$
form an orthonormal basis, and the restriction of $f$ on the real
vector space spanned by $\ket{0}$, $\ket{1'}$, and $\ket{2'}$ is
still a approximation frame function of weight~$\left(W_{l},W_{r}\right)$.
Because $f\left(\ket{0}\right)=M$, we must also have $f\left(\ket{0}\right)=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$. 
\end{proof}
\end{proof}
}

\yutsung{
\begin{proof}
~
\begin{proof}
This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.
\end{proof}
\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\end{proof}
}
